---
title: "Appendix"
subtitle: "Mental Health and Food Access"
author: "Raveena, Alanna, Jack"
date: "12/8/2021"
output: 
  html_document:
    theme: readable
    toc: true
    toc_depth: 3
    toc_float: true
---


# Load Data
```{r, echo = TRUE, message = FALSE, results = TRUE, warning = FALSE}
library(tidyverse)
library(tidycensus)
library(readxl)
library(knitr)
library(tigris)
library(sf)
library(gridExtra)
library(jtools)
library(interactions)
```

## USDA - Food Access Research Database - 2019
* Access to food options within 1 mile urban or 10 miles rural
* Percent of households using SNAP
* Poverty rate
```{r, message = FALSE, results = TRUE, warning = FALSE}
USDA <- read_csv("Food Access Research Atlas.csv") %>%
  mutate(CensusTract = case_when(str_length(as.character(CensusTract)) == 11 ~ as.character(CensusTract),
                           str_length(as.character(CensusTract)) == 10 ~ paste("0", CensusTract, sep=""),
                           TRUE ~ "not a tract")) %>%
  mutate(pct_SNAP = TractSNAP / OHU2010) %>%
  filter(CensusTract != "not a tract") %>%
  filter(pct_SNAP != "Inf") %>%
  rename(GEOID = CensusTract)%>%
  select(GEOID, pct_SNAP, PovertyRate, LA1and10)
```

The USDA food access data can be found at the following link: https://www.ers.usda.gov/webdocs/DataFiles/80591/FoodAccessResearchAtlasData2019.xlsx?v=7722
A .gitignore file was used due to the file size.

## Census Data - 2010
* Education
* Median Income
* Households with children
* Race
* Age
```{r, message = FALSE, results = FALSE, warning = FALSE}

all_states <- c(state.abb)

censusMedAge <- get_decennial(geography = "tract", 
                        year = 2010,
                        variables = c(MedAge = "P013001"),
                        output = "wide",
                        state = all_states,
                        geometry = TRUE)%>%
  select(GEOID,MedAge)
  
censusChildren <- get_decennial(geography = "tract", 
                        year = 2010,
                        variables = c(TotalUnits = "H019001",
                                      OwnWChildren = "H019003",
                                      RentWChildren = "H019006"),
                        output = "wide",
                        state = all_states,
                        geometry = FALSE)%>%
  mutate(UnitsWChildren = OwnWChildren + RentWChildren) %>%
  mutate(pct_UnitsWChildren = UnitsWChildren / TotalUnits) %>%
  select(GEOID, pct_UnitsWChildren)

censusRace <- get_decennial(geography = "tract", 
                        year = 2010,
                        variables = c(RTotal = "P010001",
                                      RWhite = "P010002",
                                      RBlack = "P010003",
                                      RAI = "P010004",
                                      RAsian = "P010005",
                                      RNH = "P010006",
                                      ROther = "P010007",
                                      RTwoPlus = "P010008"),
                        output = "wide",
                        state = all_states,
                        geometry = FALSE)%>%
  mutate(pct_RWhite = RWhite / RTotal) %>%
  mutate(pct_RBlack = RBlack / RTotal) %>%
  mutate(pct_RAI = RAI / RTotal) %>%
  mutate(pct_RAsian = RAsian / RTotal) %>%
  mutate(pct_RNH = RNH / RTotal) %>%
  mutate(pct_ROther = ROther / RTotal) %>%
  mutate(pct_RTwoPlus = RTwoPlus / RTotal) %>%
  select(GEOID, pct_RWhite, pct_RBlack, pct_RAI, pct_RAsian, pct_RNH, pct_ROther, pct_RTwoPlus)

acsEducation<- get_acs(geography = "tract", 
                   variables = c(EdTotal = "B15003_001",
                                 EdHighSchool = "B15003_017",
                                 EdGED = "B15003_018",
                                 EdAssociates = "B15003_021",
                                 EdBachelors = "B15003_022",
                                 EdMasters = "B15003_023",
                                 EdProfessional = "B15003_024",
                                 EdDoctorate = "B15003_025"), 
                   state = all_states,
                   output = "wide",
                   geometry = FALSE)%>%
  mutate(pct_EdHighSchool = EdHighSchoolE / EdTotalE)%>%
  mutate(pct_EdGED = EdGEDE / EdTotalE)%>%
  mutate(pct_EdAssociates = EdAssociatesE / EdTotalE)%>%
  mutate(pct_EdBachelors = EdBachelorsE / EdTotalE)%>%
  mutate(pct_EdMasters = EdMastersE / EdTotalE)%>%
  mutate(pct_EdProfessional = EdProfessionalE / EdTotalE)%>%
  mutate(pct_EdDoctorate = EdDoctorateE / EdTotalE)%>%
  select(GEOID, pct_EdHighSchool, pct_EdGED, pct_EdAssociates, pct_EdBachelors, pct_EdMasters, pct_EdProfessional, pct_EdDoctorate)

acsEducation_mod <- data.frame(acsEducation$pct_EdHighSchool, acsEducation$pct_EdGED, acsEducation$pct_EdAssociates, acsEducation$pct_EdBachelors, acsEducation$pct_EdMasters, acsEducation$pct_EdProfessional, acsEducation$pct_EdDoctorate)%>%
  rename(
    "High School" = acsEducation.pct_EdHighSchool,
    "GED" = acsEducation.pct_EdGED,
    "Associates" = acsEducation.pct_EdAssociates,
    "Bachelors" = acsEducation.pct_EdBachelors,
    "Masters" = acsEducation.pct_EdMasters,
    "Professional" = acsEducation.pct_EdProfessional,
    "Doctorate" = acsEducation.pct_EdDoctorate
  )
MaxEd <- colnames(acsEducation_mod)[max.col(acsEducation_mod,ties.method = "first")]
acsEducation <- mutate(acsEducation, MaxEd)%>%
  select(GEOID, MaxEd)

acsMedIncome<- get_acs(geography = "tract", 
                   variables = c(MedIncome = "B06011_001"), 
                   state = all_states,
                   output = "wide",
                   geometry = FALSE)%>%
  select(GEOID, MedIncomeE)
```

## CDC - PLACES - 2018
* Mental Health Outcomes (Mental health not good for >=14 days among adults aged >=18 years)
```{r, message = FALSE, results = TRUE, warning = FALSE}
Mental_Health <- read_csv("PLACES__Local_Data_for_Better_Health__Census_Tract_Data_2020_release (1).csv") %>%
  filter(Year == 2018) %>%
  filter(Short_Question_Text == "Mental Health") %>%
  rename(GEOID = LocationID) %>%
  group_by(GEOID) %>%
  select(GEOID, Data_Value)


Mental_Health <- Mental_Health %>%
  mutate(pct_PMH = Data_Value / 100) %>%
  select(GEOID, pct_PMH)


```
The CDC PLACES data can be found at the following link: https://chronicdata.cdc.gov/500-Cities-Places/PLACES-Local-Data-for-Better-Health-Census-Tract-D/cwsq-ngmh
A .gitignore file was used due to the file size.

## Combine Data into One Table
```{r, message = FALSE, warning = FALSE}
data <- left_join(USDA, Mental_Health) %>%
  left_join(censusMedAge)%>%
  left_join(censusChildren) %>%
  left_join(censusRace) %>%
  left_join(acsEducation) %>%
  left_join(acsMedIncome)

kable(head(data))
```


# Descriptive Statistics

### Mental Health
```{r, echo = TRUE, message = FALSE, results = TRUE, warning = FALSE}
MentalHealth_t_test <- t.test(data$pct_PMH)
MentalHealth_quartiles <- quantile(data$pct_PMH, na.rm = TRUE)
MentalHealth_st_dev <- sd(data$pct_PMH, na.rm = TRUE)
MentalHealth_hist <- ggplot(data) +
  geom_histogram(aes(x = pct_PMH),
                 bins = 30)
```

### Percent Households with Children
```{r, echo = TRUE, message = FALSE, results = TRUE, warning = FALSE}
children_t_test <- t.test(data$pct_UnitsWChildren)
children_quartiles <- quantile(data$pct_UnitsWChildren, na.rm = TRUE)
children_st_dev <- sd(data$pct_UnitsWChildren, na.rm = TRUE)
children_hist <- ggplot(data) +
  geom_histogram(aes(x = pct_UnitsWChildren),
                 bins = 30)
```

### Race
```{r, echo = TRUE, message = FALSE, results = TRUE, warning = FALSE}
RWhite_t_test <- t.test(data$pct_RWhite)
RBlack_t_test <- t.test(data$pct_RBlack)
RAI_t_test <- t.test(data$pct_RAI)
RAsian_t_test <- t.test(data$pct_RAsian)
RNH_t_test <- t.test(data$pct_RNH)
ROther_t_test <- t.test(data$pct_ROther)
RTwoPlus_t_test <- t.test(data$pct_RTwoPlus)

RWhite_quartiles <- quantile(data$pct_RWhite, na.rm = TRUE)
RBlack_quartiles <- quantile(data$pct_RBlack, na.rm = TRUE)
RAI_quartiles <- quantile(data$pct_RAI, na.rm = TRUE)
RAsian_quartiles <- quantile(data$pct_RAsian, na.rm = TRUE)
RNH_quartiles <- quantile(data$pct_RNH, na.rm = TRUE)
ROther_quartiles <- quantile(data$pct_ROther, na.rm = TRUE)
RTwoPlus_quartiles <- quantile(data$pct_RTwoPlus, na.rm = TRUE)

RWhite_st_dev <- sd(data$pct_RWhite, na.rm = TRUE)
RBlack_st_dev <- sd(data$pct_RBlack, na.rm = TRUE)
RAI_st_dev <- sd(data$pct_RAI, na.rm = TRUE)
RAsian_st_dev <- sd(data$pct_RAsian, na.rm = TRUE)
RNH_st_dev <- sd(data$pct_RNH, na.rm = TRUE)
ROther_st_dev <- sd(data$pct_ROther, na.rm = TRUE)
RTwoPlus_st_dev <- sd(data$pct_RTwoPlus, na.rm = TRUE)

RWhite_hist <- ggplot(data) +
  geom_histogram(aes(x = pct_RWhite),
                 bins = 30)
RBlack_hist <- ggplot(data) +
  geom_histogram(aes(x = pct_RBlack),
                 bins = 30)
RAI_hist <- ggplot(data) +
  geom_histogram(aes(x = pct_RAI),
                 bins = 30)
RAsian_hist <- ggplot(data) +
  geom_histogram(aes(x = pct_RAsian),
                 bins = 30)
RNH_hist <- ggplot(data) +
  geom_histogram(aes(x = pct_RNH),
                 bins = 30)
ROther_hist <- ggplot(data) +
  geom_histogram(aes(x = pct_ROther),
                 bins = 30)
RTwoPlus_hist <- ggplot(data) +
  geom_histogram(aes(x = pct_RTwoPlus),
                 bins = 30)
```


### Poverty Rate
```{r, echo = TRUE, message = FALSE, results = TRUE, warning = FALSE}
pov_t_test <- t.test(data$PovertyRate)
pov_quartiles <- quantile(data$PovertyRate, na.rm = TRUE)
pov_st_dev <- sd(data$PovertyRate, na.rm = TRUE)
pov_hist <- ggplot(data) +
  geom_histogram(aes(x = PovertyRate),
                 bins = 30)
```


### Percent Households using SNAP
```{r, echo = TRUE, message = FALSE, results = TRUE, warning = FALSE}
SNAP_t_test <- t.test(data$pct_SNAP)
SNAP_quartiles <- quantile(data$pct_SNAP, na.rm = TRUE)
SNAP_st_dev <- sd(data$pct_SNAP, na.rm = TRUE)
SNAP_hist <- ggplot(data) +
  geom_histogram(aes(x = pct_SNAP),
                 bins = 30)
```

### Median Income
```{r, echo = TRUE, message = FALSE, results = TRUE, warning = FALSE}
income_t_test <- t.test(data$MedIncomeE)
income_quartiles <- quantile(data$MedIncomeE, na.rm = TRUE)
income_st_dev <- sd(data$MedIncomeE, na.rm = TRUE)
income_hist <- ggplot(data) +
  geom_histogram(aes(x = MedIncomeE),
                 bins = 30)
```


### Age
```{r, echo = TRUE, message = FALSE, results = TRUE, warning = FALSE}
age_t_test <- t.test(data$MedAge)
age_quartiles <- quantile(data$MedAge, na.rm = TRUE)
age_st_dev <- sd(data$MedAge, na.rm = TRUE)
age_hist <- ggplot(data) +
  geom_histogram(aes(x = MedAge),
                 bins = 30)
```


### Results for Continuous Variables
```{r, echo = TRUE, message = FALSE, results = TRUE, warning = FALSE}
cont_summary <- tibble(
  Variable = c("% Households with Children", "% White", "% Black", "% AI/AN", "% Asian", "% Hawaiian", "% Other", "% Two or More", "Median Age","Poverty Rate", "Percent Households SNAP", "Median Income", "Pct of Census Tracts with Poor Mental Health for 14 days or more"),
  `Sample mean` = c(children_t_test$estimate * 100,
                    RWhite_t_test$estimate * 100,
                    RBlack_t_test$estimate * 100,
                    RAI_t_test$estimate * 100,
                    RAsian_t_test$estimate * 100,
                    RNH_t_test$estimate * 100,
                    ROther_t_test$estimate * 100,
                    RTwoPlus_t_test$estimate * 100,
                    age_t_test$estimate,
                    pov_t_test$estimate,
                    SNAP_t_test$estimate *100,
                    income_t_test$estimate,
                    MentalHealth_t_test$estimate * 100),
  `Population mean (95% confidence) - low` = 
    c(children_t_test$conf.int[1] * 100,
                    RWhite_t_test$conf.int[1] * 100,
                    RBlack_t_test$conf.int[1] * 100,
                    RAI_t_test$conf.int[1] * 100,
                    RAsian_t_test$conf.int[1] * 100,
                    RNH_t_test$conf.int[1] * 100,
                    ROther_t_test$conf.int[1] * 100,
                    RTwoPlus_t_test$conf.int[1]* 100,
                    age_t_test$conf.int[1],
                    pov_t_test$conf.int[1],
                    SNAP_t_test$conf.int[1] *100,
                    income_t_test$conf.int[1],
                    MentalHealth_t_test$conf.int[1]*100),
  `Population mean (95% confidence) - high` =
      c(children_t_test$conf.int[2] * 100,
                    RWhite_t_test$conf.int[2] * 100,
                    RBlack_t_test$conf.int[2] * 100,
                    RAI_t_test$conf.int[2] * 100,
                    RAsian_t_test$conf.int[2] * 100,
                    RNH_t_test$conf.int[2] * 100,
                    ROther_t_test$conf.int[2] * 100,
                    RTwoPlus_t_test$conf.int[2] * 100,
                    age_t_test$conf.int[2],
                    pov_t_test$conf.int[2],
                    SNAP_t_test$conf.int[2] *100,
                    income_t_test$conf.int[2],
                    MentalHealth_t_test$conf.int[2]),
    Median = c(children_quartiles[3] * 100,
                    RWhite_quartiles[3] * 100,
                    RBlack_quartiles[3] * 100,
                    RAI_quartiles[3] * 100,
                    RAsian_quartiles[3] * 100,
                    RNH_quartiles[3] * 100,
                    ROther_quartiles[3] * 100,
                    RTwoPlus_quartiles[3]*100,
                    age_quartiles[3],
                    pov_quartiles[3],
                    SNAP_quartiles[3] *100,
                    income_quartiles[3],
                    MentalHealth_quartiles[3] *100),
    `Interquartile range` = c((children_quartiles[4] - children_quartiles[2]) * 100,
                              (RWhite_quartiles[4] - RWhite_quartiles[2]) * 100,
                              (RBlack_quartiles[4] - RBlack_quartiles[2]) * 100,
                              (RAI_quartiles[4] - RAI_quartiles[2]) * 100,
                              (RAsian_quartiles[4] - RAsian_quartiles[2]) * 100,
                              (RNH_quartiles[4] - RNH_quartiles[2]) * 100,
                              (ROther_quartiles[4] - ROther_quartiles[2]) * 100,
                              (RTwoPlus_quartiles[4] - RTwoPlus_quartiles[2]) * 100,
                              age_quartiles[4] - age_quartiles[2],
                              pov_quartiles[4] - pov_quartiles[2],
                              (SNAP_quartiles[4] - SNAP_quartiles[2]) *100,
                               income_quartiles[4] - income_quartiles[2],
                              (MentalHealth_quartiles[4] - MentalHealth_quartiles[2]) *100),
   `Standard deviation` = c(children_st_dev * 100,
                            RWhite_st_dev * 100,
                            RBlack_st_dev * 100,
                            RAI_st_dev * 100,
                            RAsian_st_dev * 100,
                            RNH_st_dev * 100,
                            ROther_st_dev * 100,
                            RTwoPlus_st_dev * 100,
                            age_st_dev,
                            pov_st_dev,
                            SNAP_st_dev,
                            income_st_dev,
                            MentalHealth_st_dev * 100))

kable(cont_summary, digits = 0)
```

## Histograms for Continuous Variables
```{r warning = FALSE, echo = TRUE, message = FALSE, results = TRUE}
pretty_children_hist <- children_hist +
  theme_bw() +
  scale_x_continuous(name = "% Households with Children") +
  scale_y_continuous(name = "Number of Census Tracts") +
  theme(text = element_text(size=6),axis.text.x = element_text(angle = 90))

pretty_RWhite_hist <- RWhite_hist +
  theme_bw() +
  scale_x_continuous(name = "% White Only") +
  scale_y_continuous(name = "Number of Census Tracts") +
  theme(text = element_text(size=6),axis.text.x = element_text(angle = 90))

pretty_RBlack_hist <- RBlack_hist +
  theme_bw() +
  scale_x_continuous(name = "% Black Only") +
  scale_y_continuous(name = "Number of Census Tracts") +
  theme(text = element_text(size=6),axis.text.x = element_text(angle = 90))

pretty_RAI_hist <- RAI_hist +
  theme_bw() +
  scale_x_continuous(name = "% AI/AN Only") +
  scale_y_continuous(name = "Number of Census Tracts") +
  theme(text = element_text(size=6),axis.text.x = element_text(angle = 90))

pretty_RAsian_hist <- RAsian_hist +
  theme_bw() +
  scale_x_continuous(name = "% Asian Only") +
  scale_y_continuous(name = "Number of Census Tracts") +
  theme(text = element_text(size=6),axis.text.x = element_text(angle = 90))

pretty_RNH_hist <- RNH_hist +
  theme_bw() +
  scale_x_continuous(name = "% Hawiian Only") +
  scale_y_continuous(name = "Number of Census Tracts") +
  theme(text = element_text(size=6),axis.text.x = element_text(angle = 90))

pretty_ROther_hist <- ROther_hist +
  theme_bw() +
  scale_x_continuous(name = "% Other") +
  scale_y_continuous(name = "Number of Census Tracts") +
  theme(text = element_text(size=6),axis.text.x = element_text(angle = 90))

pretty_RTwoPlus_hist <- RTwoPlus_hist +
  theme_bw() +
  scale_x_continuous(name = "% Two or More") +
  scale_y_continuous(name = "Number of Census Tracts") +
  theme(text = element_text(size=6),axis.text.x = element_text(angle = 90))

pretty_age_hist <- age_hist +
  theme_bw() +
  scale_x_continuous(name = "Median Age") +
  scale_y_continuous(name = "Number of Census Tracts") +
  theme(text = element_text(size=6),axis.text.x = element_text(angle = 90))

pretty_pov_hist <- pov_hist +
  theme_bw() +
  scale_x_continuous(name = "Median Poverty Rate") +
  scale_y_continuous(name = "Number of Census Tracts") +
  theme(text = element_text(size=6),axis.text.x = element_text(angle = 90))

pretty_SNAP_hist <- SNAP_hist +
  theme_bw() +
  scale_x_continuous(name = "Percent Households SNAP") +
  scale_y_continuous(name = "Number of Census Tracts") +
  theme(text = element_text(size=6),axis.text.x = element_text(angle = 90))

pretty_income_hist = income_hist +
  theme_bw() +
  scale_x_continuous(name = "Median Income") +
  scale_y_continuous(name = "Number of Census Tracts") +
  theme(text = element_text(size=6), axis.text.x = element_text(angle = 90)) 

pretty_MentalHealth_hist <- MentalHealth_hist +
  theme_bw() +
  scale_x_continuous(name = "Percent of Adults Reporting Negative\n Mental Health for 14+ days") +
  scale_y_continuous(name = "Number of Census Tracts") +
  theme(text = element_text(size=6),axis.text.x = element_text(angle = 90))

grid.arrange(pretty_children_hist, pretty_RWhite_hist, pretty_RBlack_hist, pretty_RAI_hist, pretty_RAsian_hist, pretty_ROther_hist, pretty_RTwoPlus_hist, pretty_age_hist, pretty_pov_hist, pretty_SNAP_hist, pretty_income_hist, pretty_MentalHealth_hist,
             ncol = 3)
```


## Bar Plots for Categorical Variables

### Access to food options within 1 mile urban or 10 miles rural
```{r, echo = TRUE, message = FALSE, results = TRUE, warning = FALSE}
pct_access <- t.test(data$LA1and10 == "0")
pct_noaccess <-  t.test(data$LA1and10 == "1")
```

### Display Access to food options within 1 mile urban or 10 miles rural
```{r, echo = TRUE, message = FALSE, warning = FALSE, results = TRUE}
cat_summary_access <- tibble(`Access to Food` = 
                              c("Access",
                                "No Access"),
                            `Sample proportion` = 
                              c(pct_access$estimate * 100,
                                pct_noaccess$estimate *100),
                            `95-percent confidence - low` = 
                              c(pct_access$conf.int[1] * 100,
                                pct_noaccess$conf.int[1] * 100),
                            `95-percent confidence - high` = 
                              c(pct_access$conf.int[2] * 100,
                                pct_noaccess$conf.int[2] * 100))

kable(cat_summary_access, digits = 0)
```

```{r, echo = TRUE, message = FALSE, warning = FALSE, results = TRUE}
ggplot(cat_summary_access) +
  geom_bar(aes(x = `Access to Food`, 
               y = `Sample proportion`),
           stat = "identity") +
  geom_errorbar(aes(x = `Access to Food`, 
               y = `Sample proportion`,
               ymin = `95-percent confidence - low`,
               ymax = `95-percent confidence - high`),
           stat = "identity") +
  scale_y_continuous(name = "Percent of Census Tracts",
                     breaks = c(0, 20, 40, 60, 80),
                     labels = c("0", "20%", "40%", "60%", "80%")) +
  theme_bw()
```

### Education
```{r, echo = TRUE, message = FALSE, results = TRUE, warning = FALSE}
pct_EdHS <- t.test(data$MaxEd == "High School")
pct_EdGED <- t.test(data$MaxEd == "GED")
pct_EdAssociates <- t.test(data$MaxEd == "Associates")
pct_EdBachelors <- t.test(data$MaxEd == "Bachelors")
pct_EdMasters <- t.test(data$MaxEd == "Masters")
pct_EdProfessional <- t.test(data$MaxEd == "Professional")
pct_EdDoctorate <- t.test(data$MaxEd == "Doctorate")
```

### Display Education
```{r, echo = TRUE, message = FALSE, warning = FALSE, results = TRUE}
cat_summary_Ed <- tibble(`Educational Attainment` = 
                              c("High School",
                                "GED",
                                "Associates",
                                "Bachelors",
                                "Masters",
                                "Professional",
                                "Doctorate"),
                            `Sample proportion` = 
                              c(pct_EdHS$estimate * 100,
                                pct_EdGED$estimate * 100,
                                pct_EdAssociates$estimate * 100,
                                pct_EdBachelors$estimate * 100,
                                pct_EdMasters$estimate * 100,
                                pct_EdProfessional$estimate * 100,
                                pct_EdDoctorate$estimate * 100),
                            `95-percent confidence - low` = 
                              c(pct_EdHS$conf.int[1] * 100,
                                pct_EdGED$conf.int[1] * 100,
                                pct_EdAssociates$conf.int[1] * 100,
                                pct_EdBachelors$conf.int[1] * 100,
                                pct_EdMasters$conf.int[1] * 100,
                                pct_EdProfessional$conf.int[1] * 100,
                                pct_EdDoctorate$conf.int[1] * 100),
                            `95-percent confidence - high` = 
                              c(pct_EdHS$conf.int[2] * 100,
                                pct_EdGED$conf.int[2] * 100,
                                pct_EdAssociates$conf.int[2] * 100,
                                pct_EdBachelors$conf.int[2] * 100,
                                pct_EdMasters$conf.int[2] * 100,
                                pct_EdProfessional$conf.int[2] * 100,
                                pct_EdDoctorate$conf.int[2] * 100))

kable(cat_summary_Ed, digits = 0)
```

```{r, echo = TRUE, message = FALSE, warning = FALSE, results = TRUE}
ggplot(cat_summary_Ed) +
  geom_bar(aes(x = `Educational Attainment`, 
               y = `Sample proportion`),
           stat = "identity") +
  geom_errorbar(aes(x = `Educational Attainment`, 
               y = `Sample proportion`,
               ymin = `95-percent confidence - low`,
               ymax = `95-percent confidence - high`),
           stat = "identity") +
  scale_y_continuous(name = "Percent of Census Tracts",
                     breaks = c(0, 20, 40, 60, 80),
                     labels = c("0", "20%", "40%", "60%", "80%")) +
  theme_bw()
```


# Multivariate Regression
```{r, , echo = TRUE, message = FALSE, results = TRUE, warning = FALSE}
full_model <- lm(pct_PMH ~ pct_SNAP + PovertyRate + MedIncomeE + MedAge + pct_UnitsWChildren + pct_RWhite + pct_RBlack + pct_RAI + pct_RAsian + pct_RNH + pct_RTwoPlus+ LA1and10 + MaxEd, data)

summary(full_model)
```

# Transformations
```{r, echo = TRUE, message = FALSE, results = TRUE, warning = FALSE}
coeff_names <- c("Constant" = "(Intercept)",
                 "SNAP Utilization" = "pct_SNAP",
                 "Poverty Rate" = "PovertyRate",
                 "Median Age" = "MedAge",
                 "Median Income" = "MedIncomeE",
                 "Doubling Median Income" = "log2_MedIncome",
                 "% Units with Children" = "pct_UnitsWChildren",
                 "% White" = "pct_RWhite",
                 "% Black" = "pct_RBlack",
                 "% AI" = "pct_RAI",
                 "% Asian" = "pct_RAsian",
                 "% NH" = "pct_RNH",
                 "% Two Plus Races" = "pct_RTwoPlus",
                 "Access to Food (1 Mile Urban and 10 Miles Rural)" = "LA1and10")

scaled_data <- data %>%
  mutate(pct_SNAP = pct_SNAP / 100,
         PovertyRate = PovertyRate / 100,
         MedIncomeE = MedIncomeE / 1000000,
         MedAge = MedAge / 10,
         pct_UnitsWChildren = pct_UnitsWChildren / 100,
         pct_RWhite = pct_RWhite / 100,
         pct_RBlack = pct_RBlack / 100,
         pct_RAI = pct_RAI / 100,
         pct_RAsian = pct_RAsian / 100,
         pct_RNH = pct_RNH / 100,
         pct_RTwoPlus = pct_RTwoPlus / 100)

scaled_model <- lm(pct_PMH ~ pct_SNAP + PovertyRate + MedIncomeE + MedAge + pct_UnitsWChildren + pct_RWhite + pct_RBlack + pct_RAI + pct_RAsian + pct_RNH + pct_RTwoPlus+ LA1and10 + MaxEd, scaled_data)

scaled_data_medIncome_log <- scaled_data %>%
  mutate(log2_MedIncome = log(MedIncomeE, base = 2))
              

scaled_MedIncome_model_log <- lm(pct_PMH ~ pct_SNAP + PovertyRate + log2_MedIncome + MedAge + pct_UnitsWChildren + pct_RWhite + pct_RBlack + pct_RAI + pct_RAsian + pct_RNH + pct_RTwoPlus+ LA1and10 + MaxEd, data = scaled_data_medIncome_log)


export_summs(full_model, scaled_model, scaled_MedIncome_model_log,
             error_format = "(p = {p.value})",
             error_pos = "same",
             model.names = c("Initial", 
                             "Scaled Data",
                             "Median Income Logged"),
             coefs = coeff_names)
```

# Interactions
``` {r, echo = TRUE, message = FALSE, results = TRUE, warning = FALSE}
coeff_names_interaction <- c("Constant" = "(Intercept)",
                 "SNAP Utilization" = "pct_SNAP",
                 "Poverty Rate" = "PovertyRate",
                 "Median Age" = "MedAge",
                 "Median Income" = "MedIncomeE",
                 "Doubling Median Income" = "log2_MedIncome",
                 "% Units with Children" = "pct_UnitsWChildren",
                 "% White" = "pct_RWhite",
                 "% Black" = "pct_RBlack",
                 "% AI" = "pct_RAI",
                 "% Asian" = "pct_RAsian",
                 "% NH" = "pct_RNH",
                 "% Two Plus Races" = "pct_RTwoPlus",
                 "Access to Food (1 Mile Urban and 10 Miles Rural)" = "LA1and10")
                   
                   
interaction_SNAP_access_model <- lm(pct_PMH ~ pct_SNAP + PovertyRate + log2_MedIncome + MedAge + pct_UnitsWChildren + pct_RWhite + pct_RBlack + pct_RAI + pct_RAsian + pct_RNH + pct_RTwoPlus+ LA1and10 + MaxEd + pct_SNAP*LA1and10, data = scaled_data_medIncome_log)

export_summs(scaled_MedIncome_model_log, interaction_SNAP_access_model,
             error_format = "(p = {p.value})",
             error_pos = "same",
             model.names = c("Median Income Logged",
                             "Income and Access Interaction"))

interact_plot(interaction_SNAP_access_model, pred = pct_SNAP, modx = LA1and10,
              interval = TRUE) +
  scale_x_continuous(name = "Percent SNAP Usage") +
  scale_y_continuous(name = "Percent of Adults Experiencing Poor\n Mental Health 14 days or more")
```


# Results
```{r, echo = TRUE, message = FALSE, warning = FALSE}
export_summs(full_model, scaled_MedIncome_model_log, interaction_SNAP_access_model,
             error_format = "(p = {p.value})",
             error_pos = "same",
             model.names = c("Initial", 
                             "Median Income Logged",
                             "Median Income Logged and SNAP:Food Access Interaction"),
             coeffs = coeff_names_interaction)
```
