---
title: "Assignment 1+2"
author: "Raveena, Alanna, Jack"
date: "10/25/2021"
output: html_document:
  theme: readable
  toc: true
  toc_depth: 3
  toc_float: true
---

# Research Question
How do food access and demographic characteristics impact mental and physical health on a county scale?

# Prior Research
Seligman and Schillinger (2010) posit that food insecurity and chronic disease follows a cyclical pattern where food insecurity leads to chronic disease, thereby increasing medical costs and causing low income households to make trade-offs in spending, often leading to less money available to address food insecurity. Additionally, the results of Jones (2017) suggests that individual food insecurity is associated with poorer mental health and specific psychosocial stressors across global regions independent of socio-ecoomic status.

# Data
The sample population for this study is the full set of all census tracts in the United States, for all people over the age of 18. The analysis will include the following variables:

Categorical
* Access to food options within 1 mile urban or 10 miles rural
* Education
* Race
* Mental Health Outcomes

Continuous
* Percent of households using SNAP
* Poverty rate
* Median income
* Pct households with children
* Age

# Load Data
```{r, message = FALSE, results = FALSE}
library(tidyverse)
library(tidycensus)
library(readxl)
library(knitr)
library(tigris)
library(sf)
library(gridExtra)
```

## USDA - Food Access Research Database - 2019
* Access to food options within 1 mile urban or 10 miles rural
* Percent of households using SNAP
* Poverty rate
```{r, message = FALSE, results = FALSE, warning = FALSE}
USDA <- read_csv("Food Access Research Atlas.csv") %>%
  mutate(CensusTract = case_when(str_length(as.character(CensusTract)) == 11 ~ as.character(CensusTract),
                           str_length(as.character(CensusTract)) == 10 ~ paste("0", CensusTract, sep=""),
                           TRUE ~ "not a tract")) %>%
  mutate(pct_SNAP = TractSNAP / OHU2010) %>%
  filter(CensusTract != "not a tract") %>%
  filter(pct_SNAP != "Inf") %>%
  rename(GEOID = CensusTract)%>%
  select(GEOID, pct_SNAP, PovertyRate, LA1and10)
```

## Census Data - 2010
* Education
* Median Income
* Households with children
* Race
* Age
```{r, message = FALSE, results = FALSE, warning = FALSE}

all_states <- c(state.abb)

censusMedAge <- get_decennial(geography = "tract", 
                        year = 2010,
                        variables = c(MedAge = "P013001"),
                        output = "wide",
                        state = all_states,
                        geometry = TRUE)%>%
  select(GEOID,MedAge)
  
censusChildren <- get_decennial(geography = "tract", 
                        year = 2010,
                        variables = c(TotalWChildren = "H019001",
                                      OwnWChildren = "H019003",
                                      RentWChildren = "H019006"),
                        output = "wide",
                        state = all_states,
                        geometry = FALSE)%>%
  mutate(pct_OwnWChildren = OwnWChildren / TotalWChildren) %>%
  mutate(pct_RentWChildren = RentWChildren / TotalWChildren) %>%
  select(GEOID, pct_OwnWChildren, pct_RentWChildren)

censusRace <- get_decennial(geography = "tract", 
                        year = 2010,
                        variables = c(RTotal = "P010001",
                                      RWhite = "P010002",
                                      RBlack = "P010003",
                                      RAI = "P010004",
                                      RAsian = "P010005",
                                      RNH = "P010006",
                                      ROther = "P010007",
                                      RTwoPlus = "P010008"),
                        output = "wide",
                        state = all_states,
                        geometry = FALSE)%>%
  mutate(pct_RWhite = RWhite / RTotal) %>%
  mutate(pct_RBlack = RBlack / RTotal) %>%
  mutate(pct_RAI = RAI / RTotal) %>%
  mutate(pct_RAsian = RAsian / RTotal) %>%
  mutate(pct_RNH = RNH / RTotal) %>%
  mutate(pct_ROther = ROther / RTotal) %>%
  mutate(pct_RTwoPlus = RTwoPlus / RTotal) %>%
  select(GEOID, pct_RWhite, pct_RBlack, pct_RAI, pct_RAsian, pct_RNH, pct_ROther, pct_RTwoPlus)

acsEducation<- get_acs(geography = "tract", 
                   variables = c(EdTotal = "B15003_001",
                                 EdHighSchool = "B15003_017",
                                 EdGED = "B15003_018",
                                 EdAssociates = "B15003_021",
                                 EdBachelors = "B15003_022",
                                 EdMasters = "B15003_023",
                                 EdProfessional = "B15003_024",
                                 EdDoctorate = "B15003_025"), 
                   state = all_states,
                   output = "wide",
                   geometry = FALSE)%>%
  mutate(pct_EdHighSchool = EdHighSchoolE / EdTotalE)%>%
  mutate(pct_EdGED = EdGEDE / EdTotalE)%>%
  mutate(pct_EdAssociates = EdAssociatesE / EdTotalE)%>%
  mutate(pct_EdBachelors = EdBachelorsE / EdTotalE)%>%
  mutate(pct_EdMasters = EdMastersE / EdTotalE)%>%
  mutate(pct_EdProfessional = EdProfessionalE / EdTotalE)%>%
  mutate(pct_EdDoctorate = EdDoctorateE / EdTotalE)%>%
  select(GEOID, pct_EdHighSchool, pct_EdGED, pct_EdAssociates, pct_EdBachelors, pct_EdMasters, pct_EdProfessional, pct_EdDoctorate)


acsMedIncome<- get_acs(geography = "tract", 
                   variables = c(MedIncome = "B06011_001"), 
                   state = all_states,
                   output = "wide",
                   geometry = FALSE)%>%
  select(GEOID, MedIncomeE)
```

## CDC - PLACES - 2018
* Mental Health Outcomes (Mental health not good for >=14 days among adults aged >=18 years)
* Physical Health Outcomes (Physical health not good for >=14 days among adults aged >=18 years)
```{r, message = FALSE, results = FALSE, warning = FALSE}
Mental_Health <- read_csv('data/PLACES__Local_Data_for_Better_Health__Census_Tract_Data_2020_release.csv') %>%
  filter(Year == 2018) %>%
  filter(Short_Question_Text == "Mental Health") %>%
  rename(GEOID = LocationID) %>%
  group_by(GEOID) %>%
  select(GEOID, Data_Value, Data_Value_Unit)
```


## Combine Data into One Table
```{r, message = FALSE, warning = FALSE}
data <- left_join(USDA, Mental_Health) %>%
  left_join(censusMedAge)%>%
  left_join(censusChildren) %>%
  left_join(censusRace) %>%
  left_join(acsEducation) %>%
  left_join(acsMedIncome)

kable(head(data))
```
This dataset includes 72,351 census tracts across the United States.

# Descriptive Statistics
## Continuous Variables

### Percent Households with Children - Raveena

### Poverty Rate - Alanna

### Percent Households using SNAP - Jack
```{r}
SNAP_t_test <- t.test(data$pct_SNAP)
SNAP_quartiles <- quantile(data$pct_SNAP, na.rm = TRUE)
SNAP_st_dev <- sd(data$pct_SNAP, na.rm = TRUE)
SNAP_hist <- ggplot(data) +
  geom_histogram(aes(x = pct_SNAP),
                 bins = 30)
```

### Median Income - Jack
```{r}
income_t_test <- t.test(data$MedIncomeE)
income_quartiles <- quantile(data$MedIncomeE, na.rm = TRUE)
income_st_dev <- sd(data$MedIncomeE, na.rm = TRUE)
income_hist <- ggplot(data) +
  geom_histogram(aes(x = MedIncomeE),
                 bins = 30)
```

### Results for Percent Households Using SNAP and Median Income - Jack
```{r}
Jack_cont_summary <- tibble(
  Variable = c("Percent Households SNAP", 
               "Median Income"),
  `Sample mean` = c(SNAP_t_test$estimate *100,
                    income_t_test$estimate),
  `Population mean (95% confidence) - low` = 
    c(SNAP_t_test$conf.int[1] *100,
      income_t_test$conf.int[1]),
  `Population mean (95% confidence) - high` =
    c(SNAP_t_test$conf.int[2] *100,
      income_t_test$conf.int[2]),
  Median = c(SNAP_quartiles[3] *100,
             income_quartiles[3]),
  `Interquartile range` = c((SNAP_quartiles[4] - SNAP_quartiles[2]) *100,
                            income_quartiles[4] - income_quartiles[2]),
  `Standard deviation` = c(SNAP_st_dev,
                          income_st_dev))

kable(Jack_cont_summary, digits = 2)


pretty_SNAP_hist <- SNAP_hist +
  theme_bw() +
  scale_x_continuous(name = "Percent Households SNAP") +
  scale_y_continuous(name = "Number of Census Tracts") +
  theme(axis.text.x = element_text(angle = 90))

pretty_income_hist = income_hist +
  theme_bw() +
  scale_x_continuous(name = "Median Income",
                     breaks = seq(0, 100, by=50),
                     labels = seq(0, 100000, by = 50000)) +
  scale_y_continuous(name = "Number of Census Tracts") +
  theme(axis.text.x = element_text(angle = 90)) 

grid.arrange(pretty_SNAP_hist, pretty_income_hist,
             ncol = 3)
```

### Age


## Categorical Variables

### Access to food options within 1 mile urban or 10 miles rural - Jack
```{r}
pct_access <- t.test(data$LA1and10 == "0")
pct_noaccess <-  t.test(data$LA1and10 == "1")
```

### Display Access to food options within 1 mile urban or 10 miles rural - Jack
```{r}
cat_summary_access <- tibble(`Access to Food` = 
                              c("Access",
                                "No Access"),
                            `Sample proportion` = 
                              c(pct_access$estimate * 100,
                                pct_noaccess$estimate *100),
                            `95-percent confidence - low` = 
                              c(pct_access$conf.int[1] * 100,
                                pct_noaccess$conf.int[1] * 100),
                            `95-percent confidence - high` = 
                              c(pct_access$conf.int[2] * 100,
                                pct_noaccess$conf.int[2] * 100))

kable(cat_summary_access, digits = 0)

ggplot(cat_summary_access) +
  geom_bar(aes(x = `Access to Food`, 
               y = `Sample proportion`),
           stat = "identity") +
  geom_errorbar(aes(x = `Access to Food`, 
               y = `Sample proportion`,
               ymin = `95-percent confidence - low`,
               ymax = `95-percent confidence - high`),
           stat = "identity") +
  scale_y_continuous(name = "Percent of Census Tracts",
                     breaks = c(0, 20, 40, 60, 80),
                     labels = c("0", "20%", "40%", "60%", "80%")) +
  theme_bw()
```

### Education - Raveena

### Race - Raveena

### Mental Health Outcomes - Alanna








# References
Ahern, Melissa, Brown, Cheryl, Dukas, Stephen. "A National Study of the Association Between Food Environments and County-Level Health Outcomes." The Journal of Rural Health 27, no. 4 (2011): 367-379. doi: https://doi.org/10.1111/j.1748-0361.2011.00378.x

Centers for Disease Control and Prevention, "Census Tract Level State Maps of the Modified Retail Food Environment Index (mRFEI)" https://www.cdc.gov/obesity/downloads/census-tract-level-state-maps-mrfei_TAG508.pdf

Centers for Disease Control and Prevention, "PLACES: Local Data for Better Health, Census Tract Data 2020 release".
https://chronicdata.cdc.gov/500-Cities-Places/PLACES-Local-Data-for-Better-Health-Census-Tract-D/cwsq-ngmh

Jones, Andrew D."Food Insecurity and Mental Health Status: A Global Analysis of 149 Countries." American Journal of Preventative Medicine 53, no. 2 (2017): 264-273. doi: https://doi.org/10.1016/j.amepre.2017.04.008

Kaiser ML, Dionne J, Carr JK. "Predictors of Diet-Related Health Outcomes in Food-Secure and Food-Insecure Communities." Soc Work Public Health 34, no.3 (2019):214-229. doi: 10.1080/19371918.2019.1575313. Epub 2019 Feb 15. PMID: 30767652.

Seligman, Hilary K., and Dean Schillinger. "Hunger and Socioeconomic Disparities in Chronic Disease." The New England Journal of Medicine 363, no. 1 (2010): 6-9.

United States Census Bureau. American Community Survey, 5-year estimates. 2019.

United States Census Bureau. 2010.

United States Department of Agriculture. "Food Access Research Atlas". 2019. "https://www.ers.usda.gov/data-products/food-access-research-atlas/download-the-data/"
